Overlooked dynamics of algorithmic recourse

### 2022-01-11 proposal/research_proposal.Rmd
work on endogenous shifts notebook
after work on delft device

>>>>

# Introduction

In their NeurIPS 2021 paper @upadhyay2021towards demonstrate that existing approaches to algorithmic recourse are not robust to exogenous domain and model shifts. A related and so far unexplored idea is that recourse itself may lead to endogenous domain and model shifts, if a substantial share of individuals acts on it. We believe that this can have implications on the validity and cost of algorithmic recourse that have so far been overlooked.

# Related work

## @wachter2017counterfactual

## @schut2021generating

## @upadhyay2021towards

## Other

- @joshi2019towards
- @ustun2019actionable
- @karimi2021algorithmic

# Preliminary findings

## Synthetic data

## German credit data
